---
title: "[ZHANG], [XINLIN], [31421713] - Homework 3"
author: "[ZHANG], [XINLIN], [31421713]"
output: html_document
---

Please read all instructions carefully.  Fill in all fields above (Espicially your student number). To allow this file to be knit, you might need to save it in a new location, as you do not have write permissions in the dropbox folder, and R does not work well with chinese characters.
Do not comment out the lines that produce output.  Check your html file before submission to ensure it has all relevent output.



**Question 1A:**
```{r Question 1A}
Data3 <- read.csv("~/Desktop/MKT436 analytics/Homework 3/Student Data 3.csv", stringsAsFactors=FALSE)
library('earth')
```


**Question 1B:**
```{r Question 1B}
earthFit<-earth(card~.,degree=2,data=Data3)
plotmo(earthFit)
```

**Question 1C:**

From the first interaction, those with no reports and whose avergae monthly credit card expenditure is more than 103 are more likely to get the credit card.
From the second interaction, those with share of 0.039 and whose avergae monthly credit card expenditure is more than 103 are more likely to get the credit card.
From the third interaction, those with more than 6 active credit accounts and whose avergae monthly credit card expenditure is more than 103 are more likely to get the credit card.


**Question 2A:**
```{r Question 2A}
data2<-Data3[,-6]
set.seed(218)

#Generate a training set that is 80% of the data, and a validation set that is 20% 
isTraining2 = runif(nrow(data2))<.8  
data2Train = subset(data2,isTraining2)
data2Valid = subset(data2,!isTraining2)

#Function returns the RMSE using the validation set for the detailing data
getcard2RMSE = function(model){
  actualY = data2Valid$card
  predictedY = predict(model,data2Valid)
  return(mean((actualY-predictedY)^2)^.5)
}

#linear
getcard2RMSE(lm(card~reports+income+share+age+owner +dependents+months+selfemp+active+majorcards,data=data2Train))

getcard2RMSE(lm(card~reports+income+log(share)+age+owner +dependents+months+selfemp+active+majorcards,data=data2Train))

getcard2RMSE(lm(card~log(reports +1)+income+log(share)+age+owner +dependents+months+selfemp,data=data2Train))

getcard2RMSE(lm(card~log(reports +1)+income+log(share)+age+owner +dependents+months+selfemp+active+majorcards,data=data2Train))

getcard2RMSE(lm(card~log(reports +1)+log(share)+age+owner +dependents/income+months+selfemp+active+majorcards,data=data2Train))


#mars
getcard2RMSE(earth(card~.,data=data2Train))
getcard2RMSE(earth(card~.,degree=3,data=data2Train))
getcard2RMSE(earth(card~.,degree=3,thres=.001,data=data2Train))
getcard2RMSE(earth(card~.,degree=2,data=data2Train))
getcard2RMSE(earth(card~.,degree=2,thres=0,data=data2Train))  #0.3653257
getcard2RMSE(earth(card~.,degree=2,thres=.001,data=data2Train))



#K-Fold Cross Validation 
set.seed(218) 
nFold = 2
#Step 1: Randomly choose which fold each row is in 
valNum = floor(runif(nrow(data2))*nFold)+1

#Create a matrix where we store prediction error 
modelPerformance = matrix(NA,nFold,2)


for(fold in 1:nFold){
  #Step 2i: Get the training and validation data for this fold
  trainingData = subset(data2,valNum!=fold)
  validationData = subset(data2,valNum==fold)
  
  #Step 2ii: Estimate the model for this training data
  model1 = lm(card~log(reports +1)+income+log(share)+age+owner +dependents+months+selfemp+active+majorcards,data=trainingData)

  model2 = earth(card~.,degree=2,data=trainingData)

  
  #Step 2iii: Calculate out of sample MSE for this validationData
  valid1 = mean((validationData$card - predict(model1,validationData))^2)^.5
  valid2 = mean((validationData$card - predict(model2,validationData))^2)^.5

  #Store model performance
  modelPerformance[fold,] = c(valid1,valid2)
}

colMeans(modelPerformance)  #0.3787836 0.3744732

#model2's MSE is smaller than model1's MSE
chosenModel=earth(card~.,degree=2,thres=0,data=data2Train)


```



**Question 2B:**
```{r Question 2B}
#TRAIN AND ESTIMATE YOUR SECOND MODEL (WITH EXPENDITURES) HERE
set.seed(217)
#Generate a training set that is 80% of the data, and a validation set that is 20% 
isTraining = runif(nrow(Data3))<.8  
data3Train = subset(Data3,isTraining)
data3Valid = subset(Data3,!isTraining)

#Function returns the RMSE using the validation set for the detailing data
getcard3RMSE = function(model){
  actualY = data3Valid$card
  predictedY = predict(model,data3Valid)
  return(mean((actualY-predictedY)^2)^.5)
}

#linear
getcard3RMSE(lm(card~reports+income+share+age+owner +dependents+months+selfemp+active+majorcards+expenditure,data=data3Train))

getcard3RMSE(lm(card~reports+income+share+age+owner +dependents+months+selfemp+active*expenditure+majorcards,data=data3Train))

getcard3RMSE(lm(card~log(reports +1)+income+log(share)+age+owner +dependents+months+selfemp+active+majorcards+expenditure,data=data3Train))

getcard3RMSE(lm(card~log(reports +1)+log(share)+age+owner +dependents/income+months+selfemp+active+majorcards+expenditure,data=data3Train))



#mars
getcard3RMSE(earth(card~.,data=data3Train))
getcard3RMSE(earth(card~.,degree=2,data=data3Train))
getcard3RMSE(earth(card~.,degree=2,thres=0,data=data3Train))
getcard3RMSE(earth(card~.,degree=2,thres=.001,data=data3Train))
getcard3RMSE(earth(card~.,degree=3,data=data3Train))     #0.2874481
getcard3RMSE(earth(card~.,degree=3,thres=0.001,data=data3Train))     #0.2874481
getcard3RMSE(earth(card~.,degree=4,data=data3Train))      #0.2874481
getcard3RMSE(earth(card~.,degree=5,data=data3Train))      #0.2874481


#K-Fold Cross Validation 
set.seed(217) 
nFold = 2
#Step 1: Randomly choose which fold each row is in 
valNum = floor(runif(nrow(Data3))*nFold)+1

#Create a matrix where we store prediction error 
modelPerformance = matrix(NA,nFold,2)


for(fold in 1:nFold){
  #Step 2i: Get the training and validation data for this fold
  trainingData = subset(Data3,valNum!=fold)
  validationData = subset(Data3,valNum==fold)
  
  #Step 2ii: Estimate the model for this training data
  model1 = lm(card~log(reports +1)+income+log(share)+age+owner +dependents+months+selfemp+active+majorcards+expenditure,data=trainingData)
  
  model2 = earth(card~.,degree=2,thres=0,data=trainingData)
  
  
  #Step 2iii: Calculate out of sample MSE for this validationData
  valid1 = mean((validationData$card - predict(model1,validationData))^2)^.5
  valid2 = mean((validationData$card - predict(model2,validationData))^2)^.5
  
  #Store model performance
  modelPerformance[fold,] = c(valid1,valid2)
}

colMeans(modelPerformance)
# 0.3682341 0.2821581

#model2's MSE is smaller than model1's MSE
chosenModel2=earth(card~.,degree=3,data=data3Train)




```

```{r}
#Uncomment and fill in the line below to generate the RData file for submission 
save(chosenModel, chosenModel2, file='[ZHANG] [XINLIN].Rdata')
```